\rule{\textwidth}{4pt}\\[1em] \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm] Regularized Payoff Approximation in Discrete Space}\\[1em] \rule{\textwidth}{2pt}

### 2025-02-19 latex/article.tex
idea sources

Presented approach addresses these limitations by embracing the stochastic nature of markets
without imposing restrictive distributional assumptions. Instead of attempting to fit
market behavior into predetermined probability distributions as in \citep{Kuang2023}, 
this paper proposes a framework that can accommodate any empirically observed distribution. This 
distribution-free modeling approach acknowledges the complex, non-Gaussian nature of 
market price movements, which often exhibit fat tails and asymmetric behavior. It allows 
for direct incorporation of empirical distribution forecasts, enabling more accurate risk 
assessment and pricing.
Furthermore, the framework provides a flexible mechanism for extracting value from market
inefficiencies without relying on specific distributional assumptions, while being able
to adapt to changing market conditions and regime shifts that affect the shape of price
distributions.

@@

\section{Literature Review}
The theoretical foundations of option portfolio optimization were established in the work of 
\citep{Carr01012001}, which demonstrated the theoretical possibility of replicating 
arbitrary payoff functions through continuous strike spaces. While this approach 
provides elegant closed-form solutions in continuous market settings, several fundamental 
limitations affect practical implementation: the discrete availability of strike prices 
in real markets, liquidity constraints, non-negligible transaction costs scaling with 
portfolio complexity, and numerical stability challenges in finite difference implementations. 
The proposed method addresses these limitations through regularization techniques and 
discrete optimization methods tailored for real-world trading environments, while 
preserving the theoretical elegance of the original framework.

>>>>

The presented approach addresses these limitations by embracing the stochastic nature of markets
without imposing restrictive distributional assumptions. Instead of attempting to fit
market behavior into predetermined probability distributions as in \citep{Kuang2023} and 
\citep{Li2023}, this paper proposes a framework that can accommodate any empirically 
observed distribution. This distribution-free modeling approach acknowledges the complex, 
non-Gaussian nature of market price movements, which often exhibit fat tails and 
asymmetric behavior. It allows for direct incorporation of empirical distribution forecasts, 
enabling more accurate risk assessment and pricing.
Furthermore, the framework provides a flexible mechanism for extracting value from market
inefficiencies without relying on specific distributional assumptions, while being able
to adapt to changing market conditions and regime shifts that affect the shape of price
distributions.

@@

\section{Literature Review}
The theoretical foundations of option portfolio optimization were established in the work of 
\citep{Carr01012001}, which demonstrated the theoretical possibility of replicating 
arbitrary payoff functions through continuous strike spaces. While this approach 
provides elegant closed-form solutions in continuous market settings, several fundamental 
limitations affect practical implementation: the discrete availability of strike prices 
in real markets, liquidity constraints, non-negligible transaction costs scaling with 
portfolio complexity, and numerical stability challenges in finite difference implementations.

The idea of modeling complete distributions rather than point estimates was inspired by recent 
advances in time series forecasting, particularly the work of \citep{ansari2024chronos}, which 
demonstrated the effectiveness of distribution-based predictions in capturing complex temporal 
patterns. While tail risk hedging has been a fundamental concept since \citep{BlackScholes1973}, 
where options were primarily used for downside protection, our approach extends this by 
considering the entire distribution shape in portfolio construction. Unlike traditional methods 
that focus solely on tail events, we propose a comprehensive framework that models and exploits 
the complete probability distribution of asset returns.

The proposed method addresses these limitations through regularization techniques and 
discrete optimization methods tailored for real-world trading environments, while 
preserving the theoretical elegance of the original framework.
